---
title: "Challenge_15"
output: html_document
---
## Deliverable 1

```{r}
library(dplyr)
mecha_df <- read.csv('MechaCar_mpg.csv')
head(mecha_df)


```

```{r}
mpg_reg <- lm(formula= mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data = mecha_df)

summary(mpg_reg)


```
The intercept, vehicle length, and ground clearance show as the biggest contributers to correlation, followed by weight, with spoiler angle and AWD having non-significant contribution. P-value of  5.35e-11 indicates that the slope is not zero. R-squared of 0.71 is decent, but still indicates that about 30% of the variation is not accounted for with these parameters.

## Deliverable 2

```{r}
Coil_tbl <- read.csv('Suspension_Coil.csv')
head(Coil_tbl)


```
```{r}

total_summary <- summarize(Coil_tbl, Mean = mean(PSI), Median = median(PSI), Variance = var(PSI), SD = sd(PSI))
total_summary

```
```{r}
lot_summary <- Coil_tbl %>% group_by(Manufacturing_Lot) %>%
  summarize(Mean = mean(PSI), Median = median(PSI), Variance = var(PSI), SD = sd(PSI))

lot_summary

```

## Deliverable 3


```{r}
all_lots <- t.test(Coil_tbl$PSI, mu = 1500)
paste('The p-value for all lots is: ',round(all_lots$p.value,4))

lot1 <- subset(Coil_tbl, Manufacturing_Lot == 'Lot1')
lot2 <- subset(Coil_tbl, Manufacturing_Lot == 'Lot2')
lot3 <- subset(Coil_tbl, Manufacturing_Lot == 'Lot3')

lot1_ttest <- t.test(lot1$PSI, mu = 1500)
lot2_ttest <- t.test(lot2$PSI, mu = 1500)
lot3_ttest <- t.test(lot3$PSI, mu = 1500)

paste('The p-value for lot 1 is:', round(lot1_ttest$p.value,4), 'The p-value for lot 2 is:', round(lot2_ttest$p.value,4), 'The p-value for lot 3 is:',round(lot3_ttest$p.value,4))



```


